---
title: "Experiments 4 Initialization"
author: "Youngseok Kim"
date: "10/01/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This .Rmd file is to reproduce the result for a figure in the paper. Results for timings can be slightly different even in the same computing machine. Also, it can be nontrivially different if you use different computing machine. But it should not be very different. Anyway, the prediction error presented below must be the same.

### Load libraries, packages and codes

We load libraries, packages and codes for the simulation and for the plotting.

```{r library, eval=FALSE}
library(Matrix); library(Rcpp); library(varbvs); library(ggplot2); library(cowplot);
library(glmnet); library(susieR); library(BGLR); library(L0Learn); library(varbvs2)
```

### Simulation setting

#### Design matrix

We will use is an independent low dimensional Gaussian ensemble design. For abbreviation, we will call this design matrix "IndepLowdimGauss". A matrix size $n = 500$ and $p = 2,000$ will be fixed. The design matrix will be generated as follows.

```{r design}
standardize = FALSE
#X                <- matrix(rnorm(500*2000), 500, 2000)
```

Note that the design matrix $X$ is not centered, and not standardized. 

## Simulation

### Null initialization, Nonzero coefficients $\beta_1,\cdots,\beta_100$.

```{r nullbest0.9, eval = FALSE}
pred11 = matrix(0,20,9)
t11    = matrix(0,20,9)
null11 = double(20)
best11 = double(20)
sigma11 = sqrt(50 / 9)

for (i in 1:20) {
  set.seed(2010 + i)
  data              = list(X = matrix(rnorm(1000*2000), 1000, 2000))
  n.total           = dim(data$X)[1];
  p                 = dim(data$X)[2]
  train.index       = sample(n.total, floor(n.total * 0.5))
  test.index        = (1:n.total)[-train.index]
  X                 = data$X[train.index,]
  X.test            = data$X[test.index,]
  beta              = rnorm(p) * 2
  sa2               = (sqrt(1.5)^(0:19) - 1)^2
  sigma             = sqrt(sum(beta^2) / 9)
  y                <- X %*% beta + sigma * rnorm(500)
  err.test          = sigma * rnorm(500)
  y.test           <- X.test %*% beta + err.test
  null11[i]         = norm(y.test, '2')
  best11[i]         = norm(err.test, '2')
  
  cat("pve =", mean((X %*% beta)^2) / mean(y^2),"\n")
  
  t.susie           = system.time(
  fit.susie        <- susie(X = X, Y = y, standardize = standardize))
  fit.susie$beta    = coef(fit.susie)[-1]
  t.lasso           = system.time(
  fit.lasso        <- cv.glmnet(x = X, y = y, standardize = standardize))
  fit.lasso$beta    = coef(fit.lasso)[-1]
  
  t.mrash           = system.time(
  fit.mrash        <- mr_ash(X = X, y = y, sa2 = sa2,
                             stepsize = 1, max.iter = 2000,
                             standardize = standardize,
                             tol = list(epstol = 1e-12, convtol = 1e-8)))
  
  t.ridge           = system.time(
  fit.ridge        <- cv.glmnet(x = X, y = y, alpha = 0, standardize = standardize))
  fit.ridge$beta    = coef(fit.ridge)[-1]
  t.enet = system.time(
  fit.enet         <- cv.glmnet(x = X, y = y, alpha = 0.9, standardize = standardize))
  fit.enet$beta     = coef(fit.enet)[-1]
  t.blasso          = system.time(
  fit.blasso       <- BGLR(y, ETA = list(list(X = X, model="BL", standardize = standardize)), verbose = FALSE))
  fit.blasso$beta   = fit.blasso$ETA[[1]]$b
  t.bayesB          = system.time(
  fit.bayesB       <- BGLR(y, ETA = list(list(X = X, model="BayesB", standardize = standardize)), verbose = FALSE))
  fit.bayesB$beta   = fit.blasso$ETA[[1]]$b * fit.bayesB$ETA[[1]]$d
  t.varbvs          = system.time(
  fit.varbvs       <- varbvs(X, Z = NULL, y, verbose = FALSE));
  fit.varbvs$beta   = rowSums(fit.varbvs$alpha * fit.varbvs$mu)
  t.L0Learn         = system.time(
  fit.L0Learn      <- L0Learn.cvfit(X, y, nFolds=10))
  lambda.min        = fit.L0Learn$fit$lambda[[1]][which.min(fit.L0Learn$cvMeans[[1]])]
  pred11[i,] =  c("mrash"      = norm(y.test - predict(fit.mrash, X.test), '2'),
                 "susie"      = norm(y.test - predict(fit.susie, X.test), '2'),
                 "varbvs"     = norm(y.test - predict(fit.varbvs, X.test), '2'),
                 "L0Learn"    = norm(y.test - predict(fit.L0Learn, newx = X.test, lambda = lambda.min)@x, '2'),
                 "lasso"      = norm(y.test - predict(fit.lasso$glmnet.fit, newx = X.test,
                                                      s = fit.lasso$lambda.1se), '2'),
                 "ridge"      = norm(y.test - predict(fit.ridge$glmnet.fit, newx = X.test,
                                                      s = fit.ridge$lambda.1se), '2'),
                 "enet"       = norm(y.test - predict(fit.enet$glmnet.fit, newx = X.test,
                                                      s = fit.enet$lambda.1se), '2'),
                 "blasso"     = norm(y.test - X.test %*% fit.blasso$beta, '2'),
                 "bayesB"     = norm(y.test - X.test %*% fit.bayesB$beta, '2'))
  t11[i,] =     c("mrash"     = t.mrash[3],
                 "susie"      = t.susie[3],
                 "varbvs"     = t.varbvs[3],
                 "L0Learn"    = t.L0Learn[3],
                 "lasso"      = t.lasso[3],
                 "ridge"      = t.ridge[3],
                 "enet"       = t.enet[3],
                 "blasso"     = t.blasso[3],
                 "bayesB"     = t.bayesB[3])
  cat(pred11[i,],"\n")
  cat(t11[i,],"\n")
}
```