---
title: "Result_1_ENET_and_MR.ASH"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This .Rmd file is to plot results for the experiment MR.ASH versus Elastic Net (ENET). The experiment is based on the following simulation setting.

#### Design setting

We sample the standard i.i.d. Gaussian measurement $X_{ij} \sim N(0,1)$ anda construct $X \in \mathbb{R}^p$ with $n = 500$ and $p \in \{100,200,400,800,1600\}$.

#### Signal setting

We will use two different signal settings.

(1) We sample the i.i.d. normal coefficients $\beta_j \sim N(0,\sigma_\beta^2)$ for $j = 1,\cdots,p$, or $\beta \sim N(0,\sigma_\beta^2 I_p)$.

(2) We sample the i.i.d. sparse Laplace coefficients $\beta_j \sim \textrm{Laplace}(1)$ if $j \in J$ and $\beta_j = 0$ otherwise, where $J$ is a set of randomly $20$ indices in $\{1,\cdots,p\}$, chosen uniformly at random.

#### PVE

Then we sample $y = X\beta + \epsilon$, where $\epsilon \sim N(0,\sigma^2 I_n)$.

We fix PVE = 0.5, where PVE is the proportion of variance explained, defined by

$$
{\rm PVE} = \frac{\textrm{Var}(X\beta)}{\textrm{Var}(X\beta) + \sigma^2},
$$
where $\textrm{Var}(a)$ denotes the sample variance of $a$ calculated using R function `var`. To this end, we set $\sigma^2 = \textrm{Var}(X\beta)$.

#### Elastic Net

The `glmnet` R package provides an elastic net implementation. It seeks to minimize the following objective function.

$$
\frac{1}{2n} \| y - X\beta \|^2 + \lambda \left(\alpha \|\beta\|_1 + 0.5 (1 - \alpha) \|\beta\|_2^2 \right)
$$

$\lambda$ and $\alpha$ are tuning parameters. For a fixed $\alpha$ in $\{ 0.1 * (a-1) : a = 1,\cdots, 11$, we run `cv.glmnet` with the default setting to tune $\lambda$ by cross-validation. Then we select a best tuple of $\alpha$ and $\lambda$ that minimizes the cross-validation error.

#### Packages / Libraries

```{r ggplot, message = FALSE}
library(ggplot2); library(cowplot);

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}
```

## Results

#### Signal Shape 1: Normal

Let us recall that we sample the i.i.d. normal coefficients $\beta_j \sim N(0,\sigma_\beta^2)$ for $j = 1,\cdots,p$, or $\beta \sim N(0,\sigma_\beta^2 I_p)$.

We expect that in this simulation setting, the ridge regression with the optimal tuning parameter $\lambda$ will perform the best.

$$
p(\beta|y,X,\sigma^2) \propto p(y|X,\beta,\sigma^2) p(\beta) \propto \exp\left( - \frac{1}{2\sigma^2} \|y - X\beta\|_2^2 - \frac{1}{2\sigma_\beta^2} \|\beta\|_2^2 \right)
$$

This implies that $p(\beta|y,X,\sigma^2)$ is again a multivariate normal distribution and thus the posterior mode is equal to the posterior mean. Thus the optimal $\lambda$ is $\sigma^2 / (n\sigma_\beta^2)$. 

```{r fig1}
dat1 = readRDS("results/Experiment_1_Ridge.RDS")
sdat = data.frame()
for (i in 1:5) {
  dmat       = matrix(dat1[[i]]$rmse, 20, 14)
  nrmse      = colMeans(dmat / dat1[[i]]$sigma)[c(1,2,12,13,14)]
  time       = colMeans(matrix(dat1[[i]]$t, 20, 14))
  time[14]   = sum(time[2:12])
  time       = time[c(1,2,12,13,14)]
  sdat       = rbind(sdat, data.frame(nrmse = nrmse, time = time, p = 100 * 2^(i-1),
                                      fit = c("MR.ASH","RIDGE-CV","LASSO-CV","RIDGE-OPT","ENET-CV2")))
}
sdat$fit = factor(sdat$fit, levels =  c("MR.ASH","ENET-CV2","RIDGE-CV","LASSO-CV","RIDGE-OPT"))
p1 = ggplot(sdat) + geom_line(aes(x = p, y = nrmse, color = fit, linetype = fit)) +
  geom_point(aes(x = p, y = nrmse, color = fit, shape = fit), size = 2.5) +
  theme_cowplot(font_size = 14) +
  scale_x_continuous(trans = "log10", breaks = 100 * 2^(0:4)) +
  labs(title = "Signal: Gaussian", y = "predictior error (rmse / sigma)", x = "number of coefficients (p)") +
  theme(axis.line = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  scale_color_manual(values = gg_color_hue(6)[1:5])
p1
```

```{r fig2}
p2 = ggplot(sdat) + geom_bar(aes(x = factor(p), weight = nrmse, fill = fit),
                        position = "dodge2") +
  coord_cartesian(ylim = c(1.015,1.5)) +
  theme_cowplot(font_size = 14) +
  theme(axis.line = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Signal: Gaussian", y = "predictior error (rmse / sigma)", x = "number of coefficients (p)") +
  scale_fill_manual(values = gg_color_hue(6)[1:5])
p2
```

The above two figures display the prediction error. The prediction error we define here is

$$
\textrm{Pred.Err}(\hat\beta;y_{\rm test}, X_{\rm test}) = \frac{\textrm{RMSE}}{\sigma} = \frac{\|y_{\rm test} - X_{\rm test} \hat\beta \|}{\sqrt{n}\sigma}
$$
where $y_{\rm test}$ and $X_{\rm test}$ are test data sample in the same way. If $\hat\beta$ is fairly accurate, then we expect that $\rm RMSE$ is similar to $\sigma$. Therefore in average $\textrm{Pred.Err} \geq 1$ and the smaller the better.

The above 2 figures say that RIDGE-OPT (ridge regression with optimal choice of $\lambda$) outperforms, as expected. For the other methods, MR.ASH achieves the lowest prediction error in all cases.

```{r time1}
t1 = ggplot(sdat[-seq(4,25,5),]) + geom_line(aes(x = p, y = time, color = fit, linetype = fit)) +
  geom_point(aes(x = p, y = time, color = fit, shape = fit), size = 2.5) +
  theme_cowplot(font_size = 14) +
  scale_x_continuous(trans = "log10", breaks = 100 * 2^(0:4)) +
  labs(title = "Signal: Gaussian", y = "computation time (sec)", x = "number of coefficients (p)") +
  theme(axis.line = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  scale_color_manual(values = gg_color_hue(6)[1:5])
t1
```

#### Signal Shape 2: Sparse

Let us recall that we sample the i.i.d. sparse Laplace coefficients $\beta_j \sim \textrm{Laplace}(1)$ if $j \in J$ and $\beta_j = 0$ otherwise, where $J$ is a set of randomly $20$ indices in $\{1,\cdots,p\}$, chosen uniformly at random.

```{r fig3}
dat1 = readRDS("results/Experiment_1_Sparse.RDS")
sdat = data.frame()
for (i in 1:5) {
  dmat       = matrix(dat1[[i]]$rmse, 20, 14)
  nrmse      = colMeans(dmat / dat1[[i]]$sigma)[c(1,2,12,14)]
  time       = colMeans(matrix(dat1[[i]]$t, 20, 14))
  time[14]   = sum(time[2:12])
  time       = time[c(1,2,12,14)]
  sdat       = rbind(sdat, data.frame(nrmse = nrmse, time = time, p = 100 * 2^(i-1),
                                      fit = c("MR.ASH","RIDGE-CV","LASSO-CV","ENET-CV2")))
}
sdat$fit = factor(sdat$fit, levels =  c("MR.ASH","ENET-CV2","RIDGE-CV","LASSO-CV"))
p3 = ggplot(sdat) + geom_line(aes(x = p, y = nrmse, color = fit, linetype = fit)) +
  geom_point(aes(x = p, y = nrmse, color = fit, shape = fit), size = 2.5) +
  theme_cowplot(font_size = 14) +
  scale_x_continuous(trans = "log10", breaks = 100 * 2^(0:4)) +
  labs(title = "Signal: Normal", y = "predictior error (rmse / sigma)", x = "number of coefficients (p)") +
  theme(axis.line = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  scale_color_manual(values = gg_color_hue(6)[1:4])
p3
```

```{r fig4}
p4 = ggplot(sdat) + geom_bar(aes(x = factor(p), weight = nrmse, fill = fit),
                        position = "dodge2") +
  coord_cartesian(ylim = c(1.015,1.5)) +
  theme_cowplot(font_size = 14) +
  theme(axis.line = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Signal: SparseLaplace", y = "predictior error (rmse / sigma)", x = "number of coefficients (p)") +
  scale_fill_manual(values = gg_color_hue(6)[1:5])
p4
```

The above 2 figures say that MR.ASH achieves the lowest prediction error in all cases.

```{r time2}
t2 = ggplot(sdat) + geom_line(aes(x = p, y = time, color = fit, linetype = fit)) +
  geom_point(aes(x = p, y = time, color = fit, shape = fit), size = 2.5) +
  theme_cowplot(font_size = 14) +
  scale_x_continuous(trans = "log10", breaks = 100 * 2^(0:4)) +
  labs(title = "Signal: Gaussian", y = "computation time (sec)", x = "number of coefficients (p)") +
  theme(axis.line = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  scale_color_manual(values = gg_color_hue(6)[1:4])
t2
```

## Conclusion

```{r}
sessionInfo()
```